```{r data, include=FALSE}

library(ggplot2)
```

### City Demographics, Polling, and Budget

You are the provost of `r city_name`, elected in `r sample(2012:2021, size=1)`. 

The current population of `r city_name` (as of December 2022) is `r sample(150000:170000, size=1)`. The demographic data for the city is shown below.

```{r A1, fig.show="hold", out.width="50%", echo=FALSE, fig.cap="Inverkeld demographics (Source: Office for National Statistics)"}

Pop <- c(sample(150000:170000, size=3, replace=TRUE), sample(170000:180000, size=3, replace=TRUE), sample(190000:170000, size=2, replace=TRUE), sample(150000:170000, size=2, replace=TRUE))
PopYears <- c(2012:2021)
population <- data.frame(Pop, PopYears)
ggplot(data = population, aes(x=PopYears, y=Pop)) + 
  geom_point() +
  geom_line() +
  labs(y = "Number of Inverkeld residents (estimated)", x = "Year") +
  scale_y_continuous(limits=c(0, 200000)) + 
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())


Demog <- c((rep("Births", 10)), (rep("Deaths", 10)))
Num <- c(sample(1000:2000, size=10, replace=TRUE), sample(500:1500, size=8, replace=TRUE), sample(3000:5500, size=2, replace=TRUE))
DemogYears <- c(rep(2012:2021, 2))
birthdeath <- data.frame(Demog, Num, DemogYears)
ggplot(data = birthdeath, aes(x=DemogYears, y=Num, group=Demog, colour=Demog)) + 
  geom_point() +
  geom_line() +
  labs(y = "Number of births and deaths in Inverkeld (estimated)", x = "Year", colour = "Demographics") +
  scale_y_continuous(limits=c(0, 5500)) + 
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) + 
  scale_color_discrete(name="")
```
You were elected as a member of the popular "Environment First" party and made a number of election promises regarding a "Green New Deal" for `r city_name`. This is your first full year in office.

```{r A2, fig.cap="Voting intention by Inverkeld residents (Source: YouGov polling)", echo=FALSE}

Party <- c((rep("Revolutionary", 10)), (rep("Social Capital", 10)), (rep("Environment First", 10)), (rep("Wind Power", 10)), (rep("Social Redistribution", 10)))
Polls <- c(sample(1:3, size=10, replace=TRUE), sample(8:14, size=10, replace=TRUE), sample(15:20, size=10, replace=TRUE), sample(5:10, size=10, replace=TRUE), sample(1:2, size=10, replace=TRUE))
PolYears <- c(rep(2012:2021, 5))
politics <- data.frame(Party, Polls, PolYears)
ggplot(data = politics, aes(x=PolYears, y=Polls, color=Party)) + 
  geom_point() +
  geom_line() +
  labs(y = "Voting Intention", x = "Year") + 
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())

Councillors <- sum(politics[politics$PolYears>2020, 2])
```

There are currently `r Councillors` elected councillors, representing the 5 main political parties in `r city_name` as follows:

```{r A3, echo=FALSE}

pol2021 <- (politics[politics$PolYears>2020, 2])
Parties <- c("Revolutionary", "Social Capital", "Environment First", "Wind Power", "Social Redistribution")

Councillors <- data.frame(Parties, pol2021)

kable(x = Councillors, 
      format = "html", 
      col.names = c("Political Party", "Number of Seats"))

```
<br><br>
The overall budget (expenditures) for the 2022-2023 financial year was £`r sample(400000000:600000000, size=1)`. A summary of expeditures by category for this financial year is shown below. 

```{r A4, fig.cap="Public expenditures by category for the 2022-2023 financial year (Source: Inverkeld City Council)", echo=FALSE}

expenses <- data.frame(
  Category=c("Education", "Industry and Agriculture", "Social Care", "Transport", "Public order and safety", "Healthcare", "Housing", "Other"),
  value=c(13,7,9,5,7,21,8,2)
)

ggplot(expenses, aes(x="", y=value, fill=Category)) +
  geom_bar(stat="identity", width=1, color="white") +
  coord_polar("y", start=0) +
  theme_void() 
```



### Hospital and Hospital Budget

* You can find key information about the main hospital in `r city_name`, the `r hosp_name` in the [Hospital Dashboard](dashboardA.qmd)

The annual operating budget for financial year 2022-2023 was £1.3 million, and average expenditures are shown by category in the figure below. 

```{r A5, fig.cap="Hospital expenditures by category for financial year 2022-2023 (Source: NHS Scotland)", echo=FALSE}

expenses <- data.frame(
  Category=c("Staff costs", "Healthcare expenditures (drugs, supplies, etc.)", "Other supplies", "Other running costs (procurement, IT, HR, etc.)"),
  value=c(25,17,9,12)
)

ggplot(expenses, aes(x="", y=value, fill=Category)) +
  geom_bar(stat="identity", width=1, color="white") +
  coord_polar("y", start=0) +
  theme_void() 

```


### Epidemiological Data

`r include_statement`