```{r data4D, include=FALSE}

library(ggplot2)
library(knitr)

outbreak_deaths3D <- 11
outbreak_cases3D <- 657
outbreak_icu3D <- 18

outbreak_deaths4D <- 22
outbreak_cases4D <- 385
outbreak_icu4D <- 10

```

### Pandemic Report {.unnumbered}

*Briefing:*

* Based on collated hospital reports and death certificates, it is believed that there have been `r outbreak_deaths4D` deaths due to `r dis_name` in `r city_name` thus far

* There are currently `r outbreak_cases4D` patients in the `r hosp_name` with confirmed `r dis_name`, or symptoms consistent with `r dis_name`

* There are currently `r outbreak_icu4D`  patients currently in the ICU with confirmed `r dis_name`

* The public have been provided with health warnings and advice

* Hospital triage measures for postponing procedures and discharging patients where possible have been approved by the local NHS board and implemented

* Microbiology testing has been performed on samples from all stages of the food chain (Table 1)

Table 1. Microbiological testing of products from poultry farms and related food chain stages in the `r city_name` `r dis_name` outbreak.

<table border="1" style="border-collapse: collapse;">
  <tr>
    <th>Location</th>
    <th>Number of products tested</th>
    <th>Number of positive cultures</th>
  </tr>
  <tr>
    <td>Sue's Duck Farm</td>
    <td>`r sample(30:100, 1)`</td>
    <td>`r sample(0:10, 1)`</td>
  </tr>
  <tr>
    <td>Craig's Chickens</td>
    <td>`r sample(30:100, 1)`</td>
    <td>`r sample(0:10, 1)`</td>
  </tr>
  <tr>
    <td>MeatCo Packing Plant</td>
    <td>`r sample(50:200, 1)`</td>
    <td>`r sample(0:15, 1)`</td>
  </tr>
  <tr>
    <td>Highgrove Poultry Processing</td>
    <td>`r sample(50:150, 1)`</td>
    <td>`r sample(0:10, 1)`</td>
  </tr>
  <tr>
    <td>Clucks-alot Farms</td>
    <td>`r sample(30:100, 1)`</td>
    <td>`r sample(0:5, 1)`</td>
  </tr>
  <tr>
    <td>Lucky Clucky Farms</td>
    <td>`r sample(30:100, 1)`</td>
    <td>`r sample(0:3, 1)`</td>
  </tr>
  <tr>
    <td>The Golden Goose</td>
    <td>`r sample(30:100, 1)`</td>
    <td>`r sample(0:7, 1)`</td>
  </tr>
  <tr>
    <td>Packaged Poultry Inc.</td>
    <td>`r sample(50:200, 1)`</td>
    <td>`r sample(1:10, 1)`</td>
  </tr>
  <tr>
    <td>Lakesmere Butchers</td>
    <td>`r sample(20:70, 1)`</td>
    <td>`r sample(0:4, 1)`</td>
  </tr>
  <tr>
    <td>Heather and Gorse Farms</td>
    <td>`r sample(30:100, 1)`</td>
    <td>`r sample(0:8, 1)`</td>
  </tr>
  <tr>
    <td>Grace's Ganders</td>
    <td>`r sample(30:100, 1)`</td>
    <td>`r sample(0:5, 1)`</td>
  </tr>
  <tr>
    <td>Loosey Goosey Farms</td>
    <td>`r sample(30:100, 1)`</td>
    <td>`r sample(0:2, 1)`</td>
  </tr>
  <tr>
    <td>FoodMart Supermarket</td>
    <td>`r sample(50:200, 1)`</td>
    <td>`r sample(0:6, 1)`</td>
  </tr>
  <tr>
    <td>Greenacres</td>
    <td>`r sample(30:100, 1)`</td>
    <td>`r sample(0:3, 1)`</td>
  </tr>
  <tr>
    <td>Hill Farm</td>
    <td>`r sample(30:100, 1)`</td>
    <td>`r sample(0:7, 1)`</td>
  </tr>
  <tr>
    <td>Loyola's Turkey Farm</td>
    <td>`r sample(30:100, 1)`</td>
    <td>`r sample(0:4, 1)`</td>
  </tr>
  <tr>
    <td>Pre-Packaged Poultry Ltd.</td>
    <td>`r sample(50:200, 1)`</td>
    <td>`r sample(1:10, 1)`</td>
  </tr>
  <tr>
    <td>Goosopolis Farms</td>
    <td>`r sample(30:100, 1)`</td>
    <td>`r sample(0:5, 1)`</td>
  </tr>
  <tr>
    <td>Cordelia and Ken's Chickens</td>
    <td>`r sample(30:100, 1)`</td>
    <td>`r sample(0:6, 1)`</td>
  </tr>
  <tr>
    <td>Fair Hope Farm</td>
    <td>`r sample(30:100, 1)`</td>
    <td>`r sample(0:2, 1)`</td>
  </tr>
</table>
<br><br>


* Case investigation and patient interviews have been carried out (Table 2)
```{r data4Dfoods, include=FALSE}

# Sample foods for exposure
food_items <- c("poultry", "beef", "pork", "salad", "spinach", "apple", "bread", "milk", "cheese", 
                "potatoes", "chocolate", "fruit juice", "orange", "rice", "pasta", "yogurt", "pizza", 
                "soda", "chicken nuggets", "chips", "coffee", "beer", "tofu", "fish", "hamburger", 
                "turkey", "tomatoes", "garlic", "onion", "cabbage", "beans", "carrot", "peach", 
                "lettuce", "cucumber", "eggplant", "peanut butter", "popcorn", "canned soup", 
                "ice cream", "mushrooms", "green beans", "pancakes", "waffles", "sushi", "steak", 
                "bacon", "smoothie", "bread rolls", "salsa", "nuts", "ketchup", "mustard", 
                "hot dog", "tacos", "fried chicken", "bagels", "grapes", "doughnuts", "granola", 
                "hummus", "tomato sauce", "crackers", "avocado", "bacon", "cantaloupe", "asparagus", 
                "sardines", "clams", "cherry pie", "spinach dip", "popcorn chicken", "chicken soup", 
                "zucchini", "pita bread", "mango", "pineapple", "brownies", "cereal", "french fries", 
                "soda pop", "milkshake", "energy drink", "nachos", "apple pie", "scrambled eggs", 
                "toast", "crepes", "pie", "cheese sandwich", "fish sticks", "roast chicken", 
                "vegetable soup", "burritos", "lasagna", "ginger ale", "root beer", "apple", "banana", "carrot", "chicken breast", "beef steak", "pork chop", "salmon", 
  "turkey", "potatoes", "lettuce", "spinach", "tomato", "cucumber", "onion", "garlic", 
  "cabbage", "broccoli", "cauliflower", "green beans", "zucchini", "bell pepper", "chili pepper", 
  "avocado", "kiwi", "pear", "grapes", "orange", "strawberries", "blueberries", "mango", 
  "pineapple", "papaya", "watermelon", "apricot", "plum", "peach", "cherries", "fig", 
  "lemon", "lime", "grapefruit", "pomegranate", "coconut", "almonds", "walnuts", "pecans", 
  "hazelnuts", "cashews", "pistachios", "peanuts", "sunflower seeds", "pumpkin seeds", 
  "chia seeds", "flaxseeds", "quinoa", "rice", "pasta", "spaghetti", "couscous", "bulgur", 
  "oats", "barley", "wheat bread", "sourdough", "baguette", "croissant", "whole wheat bread", 
  "tortilla", "naan", "pita bread", "flatbread", "pizza", "burger", "hot dog", "chicken nuggets", 
  "fish fingers", "cheese", "cheddar", "mozzarella", "parmesan", "feta", "cream cheese", 
  "cottage cheese", "yogurt", "greek yogurt", "butter", "margarine", "olive oil", "vegetable oil", 
  "coconut oil", "peanut butter", "almond butter", "mayonnaise", "ketchup", "mustard", "bbq sauce", 
  "hot sauce", "soy sauce", "teriyaki sauce", "salsa", "guacamole", "hummus", "tzatziki", "pesto", 
  "balsamic vinegar", "apple cider vinegar", "white vinegar", "red wine vinegar", "rice vinegar", 
  "coconut vinegar", "fish sauce", "worcestershire sauce", "vinegar", "lemon juice", "lime juice", 
  "orange juice", "cranberry juice", "apple juice", "carrot juice", "tomato juice", "green juice", 
  "smoothie", "milk", "almond milk", "soy milk", "coconut milk", "oat milk", "chocolate milk", 
  "coffee", "tea", "green tea", "herbal tea", "black tea", "matcha", "hot chocolate", "beer", 
  "wine", "whiskey", "vodka", "gin", "rum", "tequila", "cocktail", "fruit punch", "soda", "ginger ale", 
  "lemonade", "iced tea", "sports drink", "energy drink", "sparkling water")


# Function to generate food consumption
generate_food <- function(include_poultry = FALSE) {
  # Randomly sample between 15 and 35 items
  sampled_foods <- sample(food_items, sample(15:35, 1))
  
  # Optionally add a poultry product if include_poultry is TRUE
  if (include_poultry) {
    sampled_foods <- c(sampled_foods, sample(c("chicken breast", "chicken wings", "roast chicken", "chicken sandwich", "chicken salad", "turkey sandwich", "turkey breast", "roast dinner", "roast chicken", "chicken fingers"), 1))
  }
  
  # Return the foods as a comma-separated string
  paste(sampled_foods, collapse = ", ")
}

# Generate food consumption data for patients
patients_foods <- c(
  generate_food(include_poultry = TRUE),
  generate_food(include_poultry = TRUE),
  generate_food(),
  generate_food(include_poultry = TRUE),
  generate_food(include_poultry = TRUE),
  generate_food(),
  generate_food(include_poultry = TRUE),
  generate_food(),
  generate_food(include_poultry = TRUE),
  generate_food(include_poultry = TRUE)
)

# Print the food consumption data in HTML table format
html_table <- paste0(
  "<table border='1'>
    <tr><th>Patient no.</th><th>Foods consumed (10 days prior to symptom onset)</th></tr>",
  paste0("<tr><td>", 1:10, "</td><td>", patients_foods, "</td></tr>", collapse = "\n"),
  "</table>"
)

# Output the HTML table


```


`r html_table`


