```{r email-setup4C, echo=FALSE}
# Load necessary libraries
library(randomNames)
library(stringr)

# Define generic variables for emails

closing_phrases <- c("Yours sincerely,", "Best wishes,", "Kind regards,", "All the best,", "Sincerely,", "Yours truly,", "Respectfully,")

# Generate random names for 10 authors
author_names <- randomNames(10, which.names = "both", return.complete.data = TRUE)

# Initialize an empty data frame to store names, emails, and other details
author_data <- data.frame(
  Name = character(0),
  Email = character(0),
  RandomDates = character(0),  # Initialize column for random dates
  RandomDateTime = character(0),  # Initialize column for random date and time
  stringsAsFactors = FALSE
)

# Iterate through each author's name to generate email addresses and add random dates
for (i in 1:nrow(author_names)) {
  first_name <- author_names[i, "first_name"]
  last_name <- author_names[i, "last_name"]
  
  # Concatenate all last names without spaces
  last_names_concat <- paste0(gsub(" ", "", last_name), collapse = "")
  
  # Choose a random domain for the email address
  domain <- sample(c("gmail.com", "aol.com", "yahoo.com", "msn.com", "comcast.net", "mail.com", "hotmail.co.uk", "att.net"), 1)
  
  # Choose a random method for generating the email address
  method <- sample(1:4, 1)  # Randomly select one of the methods
  
  # Initialize variable to store the email address
  email_address <- ""
  
  # Generate email address based on selected method
  if (method == 1) {
    # Method 1: Generate a plausible email address
    email_address <- paste0(tolower(substr(first_name, 1, 1)), tolower(substr(last_names_concat, 1, 1)), sprintf("%04d", sample(1:9999, 1)), "@", domain)
  } else if (method == 2) {
    # Method 2: Concatenate first and last name
    email_address <- paste0(tolower(first_name), ".", tolower(last_names_concat), "@", domain)
  } else if (method == 3) {
    # Method 3: Concatenate first initial of first name with last name
    email_address <- paste0(tolower(substr(first_name, 1, 1)), ".", tolower(last_names_concat), "@", domain)
  } else {
    # Method 4: Concatenate last name with a random number
    email_address <- paste0(tolower(last_names_concat), sample(1000:9999, 1), "@", domain)
  }
  
  # Append to the data frame
  author_data <- rbind(author_data, data.frame(Name = paste(first_name, last_name),
                                               Email = email_address,
                                               RandomDates = NA,  # Placeholder for random dates
                                               RandomDateTime = NA,  # Placeholder for random date and time
                                               stringsAsFactors = FALSE))
}

# Define the workshop4_date
workshop4_date <- as.Date("2025-03-13", format = "%Y-%m-%d")

# Generate 10 random dates within 0 to 2 days before workshop4_date
random_dates <- workshop4_date - sample(0:2, nrow(author_data), replace = TRUE)

# Format the random dates
formatted_random_dates <- format(random_dates, "%d %B %Y")

# Add formatted random dates to author_data
author_data$RandomDates <- formatted_random_dates

# Generate random hours and minutes
random_hours <- sample(1:24, nrow(author_data), replace = TRUE)
random_minutes <- sample(0:59, nrow(author_data), replace = TRUE)

# Combine random hours and minutes into HH:MM format
random_times <- paste0(random_hours, ":", sprintf("%02d", random_minutes))

# Add random times to RandomDateTime column in author_data
author_data$RandomDateTime <- random_times
```

### Emails {.unnumbered}

Your committee has recently received a great deal of correspondence regarding the pandemic in `r city_name`. A representative sample of these e-mails is shown below.

::: {.callout-caution collapse="true" icon=false}
## Email #1 {.unnumbered}
```{r email-upsetC, echo=FALSE}
# Define variables to randomise e-mail content
adjectives <- sample(c("Disgraceful", "Terrible", "Horrible", "Devastating", "Sad", "Bloody"), 1)
angry1 <-  sample(c("outraged", "upset", "so angry", "devastated", "shattered"), 1)
hope <-  sample(c("hope", "hope very much", "wish", "expect", "sincerely hope"), 1)
states_of_affairs <-  sample(c("dreadful state of affairs", "horrible pandemic", "all of the poor people dying", "tragedy"), 1)
times <-  sample(c("immediately", "very soon", "at once", "as soon as possible"), 1)
```
<b>From:</b> `r author_data$Email[1]`<br>
<b>To:</b> pandemic_response@`r city_name`.co.uk <br>
<b>Cc:</b> <br>
<b>Subject:</b> This `r adjectives` Pandemic <br>
<b>Date:</b> `r author_data$RandomDates[1]` `r author_data$RandomDateTime[1]`<br>

Dear Pandemic Response Committee

I am so frightened by the current pandemic that is rampaging through my beloved city. I have never heard of this MRSA before but it is dreadfully scary. The radio advert I heard yesterday made it sound like a huge problem. What is the world coming to, I ask you, with the MRSA plague on top of the COVID19 one already and the monkeypox as well. It feels like a judgement on our times.

Thank you so much for your hard work keeping us safe, I heard that you were buying in some vancomycin to kill these evil superbugs. I think you should distribute this to everyone in Malleith so that we can be safe from this terror.

`r sample(closing_phrases, 1)`<br> `r author_data$Name[1]`

:::

::: {.callout-caution collapse="true" icon=false}
## Email #2 {.unnumbered}

<b>From:</b> `r author_data$Email[2]`<br>
<b>To:</b> pandemic_response@`r city_name`.co.uk <br>
<b>Cc:</b> <br>
<b>Subject:</b> Save Our Hospitals<br>
<b>Date:</b> `r author_data$RandomDates[2]` `r author_data$RandomDateTime[2]`<br>


Dear Pandemic Response Committee,

I am so worried about my nan, who is going into the hospital for a hip replacement surgery this coming Sunday. She really needs it as the cartilage in her joints is completely gone and so it is very painful for her to walk. 

I am really worried that she will have caught the MRSA from the hospital and will die. I heard from Nell who is a nurse there that they have new training measures in place to try to prevent the spread of the superbug, but I am just so worried that it will not be enough. Are there any further measures that you can take to help to keep us all safe?

I know the NHS is struggling because it has been underfunded for so many years, but if you can find a little bit of extra money somewhere, I am sure it would make a real difference to my nan.


Thank you so much for all the hard work you do,<br>
`r author_data$Name[2]`

:::

::: {.callout-caution collapse="true" icon=false}
## Email #3 {.unnumbered}

<b>From:</b> `r author_data$Email[3]`<br>
<b>To:</b> pandemic_response@`r city_name`.co.uk <br>
<b>Cc:</b> <br>
<b>Subject:</b> The Collapse of Civilization<br>
<b>Date:</b> `r author_data$RandomDates[3]` `r author_data$RandomDateTime[3]`<br>

Dear Pandemic Response Committee,

It is an outrage the way that in this modern era, pandemics are being manufactured and allowed to disrupt our very way of life. Last time it was the so-called "COVID" virus and the sheer utter gall of the government trying to shut down everything that gave us pleasure in life, whether that's a simple birthday party with friends or the ability to go out to the shops without having to wear a suffocating mask. 

Now you are trying to say that in the name of "public health" we have to close all of our gyms, cinemas, and nightclubs? I find myself completely impressed by the sheer unmitigated bloody gall of it. What next - more attacks on freedom of speech, a return of masking, another forced vaccination campaign? I am also appalled by the shortsightedness of your committee's actions - have you even considered the knock-on effects of these closures? Businesses are losing money, and you can't expect the current obesity epidemic to go away if you shut all the gyms and people can't even exercise. I thought that "public health" was supposed to be about keeping people healthy!

You can be assured that I will *not* be voting for any of you when the next election comes!

`r sample(closing_phrases, 1)`<br>
`r author_data$Name[3]`

:::

::: {.callout-caution collapse="true" icon=false}
## Email #4 {.unnumbered}

<b>From:</b> `r author_data$Email[4]`<br>
<b>To:</b> pandemic_response@`r city_name`.co.uk <br>
<b>Cc:</b> <br>
<b>Subject:</b> Scared<br>
<b>Date:</b> `r author_data$RandomDates[4]` `r author_data$RandomDateTime[4]`<br>

Dear Pandemic Response Committee,

Thank you so much for your time and hard work trying to protect our beautiful city from this terrible pandemic. You hear so much nowadays about disease outbreaks in oh, just every city, and it is a real relief to hear that you are doing the hard work needed in order to keep us all safe.

I wouldn't want to take your time up, only I am very worried about my poor nan and her third husband, they have been told not to travel and I am really concerned for them. Of course I don't want them to get this dreadful disease, but seeing their grandchildren is one of the only pleasures left in their lives, they are getting on in years and they don't go out much anyways, but am I still okay to visit them? And, are we going to have another scandal in this pandemic with the care homes, the way we done with that COVID pandemic? I don't have space in my house and sure I'm working all day long, but if I need to pull my nan out of the care home to keep her safe, I am not sure how we would make that work, but I can't see how to leave her there if she's going to be infected by this horrible disease. We were that lucky that she didn't get the COVID too badly, but she's been poorly since then and I do worry.

`r sample(closing_phrases, 1)`<br>
`r author_data$Name[4]`

:::

### News/Blog Posts {.unnumbered}

```{r news4C, include=FALSE}
# Load needed libraries
library(randomNames)
library(stringr)

# Generate a paper name
paper_name <- sample(c("Times", "Courier", "Express", "Chronicle", "Gazette", "Herald", "News", "Metro", "Sentinel", "Beacon", "Journal"), 1)

# Generate journalist information (name, pronoun, e-mail address)
# Generate a random journalist name and gender
journalist <- randomNames(gender = sample(c(0, 1, 2), 1), which.names = "both", return.complete.data = TRUE)

# Extract first and last names and gender for the journalist
first_name <- journalist$first_name
last_name <- journalist$last_name
journ_name <- paste(first_name, last_name)
gender <- journalist$gender

# Generate a plausible email address
journ_email <- paste0(tolower(substr(first_name, 1, 1)), tolower(substr(last_name, 1, 1)), 
                sprintf("%04d", sample(1:9999, 1)), "@", city_name, paper_name, ".com")

# Determine pronoun based on gender
journ_pronoun <- ifelse(gender == 0, "He", ifelse(gender == 1, "She", "They"))

# Generate a random number for the contact info
generate_uk_landline_number <- function() {
  # Generate a random landline number
  area_code <- sample(c("01382", "01224", "01463", "01786", "01738", "01343"), 1)  # Sample some common area codes
  part1 <- sprintf("%04d", sample(1000:9999, 1))
  part2 <- sprintf("%04d", sample(1000:9999, 1))
  phone_number <- paste0("+44 ", area_code, " ", part1, " ", part2)
  return(phone_number)
}

# Generate a random UK landline number
landline_number <- generate_uk_landline_number()

#Define variables for the dates: 
workshop4_date <- as.Date("2025-03-13", format="%Y-%m-%d")
news_date <- workshop4_date - sample(c(3:6), 1)
news_date <- format(news_date, "%d %B, %Y")
pubdate <- news_date

# copy over variables for the pandemic stats
outbreak_deaths4C <- 25
outbreak_cases4C <- 204
outbreak_icu4C <- 7
```

Your committee has also been monitoring news and published blog posts about the pandemic in `r city_name`, in order to better gauge public opinion. A representative sample of these is shown below.

::: {.callout-caution collapse="true" icon=false}
## News/blog post #1 {.unnumbered}

<font size="+3"><b>Concerns Remain Over Outbreak of `r dis_name` in `r city_name`</b></font><br>
<font size="+2"><b>`r city_name` `r paper_name`</b></font><br>


The situation appears to be improving somewhat in `r city_name`, compared to a few weeks ago, but the city is still struggling under the wave of another pandemic, coming hard on the heels of the COVID pandemic which began nearly five years ago. 

To date there have been `r outbreak_deaths4C` deaths attributed to the pathogen, *`r inf_agent`*, and hundreds of people are currently ill with the disease.

The city's Emergency Pandemic Response Committee seems to on the ball, and their recent efforts have reduced cases, but rumours abound that this *`r inf_agent`* strain is evolving new and more deadly forms of antibiotic resistance - does this spell trouble for the city in the days to come? Doctors and scientists have been warning for years about the dangers of antimicrobial resistance, have their Cassandra-like prophecies finally come true?

News from `r city_name` is also rife with rumours that many of the city's businesses may be forced out of business due to the health measures imposed by the Emergency Pandemic Response Committee, which caused gyms, nightclubs, and cinemas to shut temporarily, and imposed extra financial burdens due to providing extra handsanitizer and cleaning equipment in supermarkets. Local business owner Darren Gilmore said, "It's been tough for every business ever since COVID hit, but I'm obviously quite worried about the pandemic that we've got going on now. My business hasn't been forced to shut, but a number of my friends, they've been closed down by this EPRC. I don't know what will happen next."

The economic costs of lockdown were a hotly debated topic during the COVID-19 pandemic, and it seems that the debate is being reignited here in `r city_name` today. Some local business owners have called for a protest, claiming that the city council has no right to impose these closures and that their civil liberties are being violated.

The Emergency Pandemic Response Committee was not available for comment. The First Minister of Scotland made a statement saying that every effort possible is being made to tackle the pandemic in `r city_name`. 

**About the Author:**

`r journ_name` is a health correspondent at the `r city_name` `r paper_name`, specializing in public health and safety issues.`r journ_pronoun` can be contacted at `r journ_email`.

:::

::: {.callout-caution collapse="true" icon=false}
## News/blog post #2 {.unnumbered}

```{r news4C2, echo=FALSE}

papername1 <- c("News", "Daily Press", "Evening News", "Star", "Telegraph", "Post", "Looking-Glass", "Sentinel", "Times")
authname1 <- c("Maurice", "Cyrus", "Aaron", "Jane", "Abigail", "Ben", "Eden", "Jessica", "Leone", "Louisa", "Louis", "Fred", "Steve", "Barbara", "Norman", "Susan", "Edwin", "Isaac", "Austin", "Hugh", "Roselyne", "Francis", "Frances", "David", "Elliot", "Alan", "Joan", "Lester", "Devendra", "Lettitia", "Clive", "Perry", "J.M.", "S.R.", "A.B.", "Frank", "Mick", "Graham", "Walter", "Tony", "Leana", "Chester", "Peter", "Ward", "Ken", "Alice", "Erin", "Kate", "Niels", "Emma", "Elena", "Mary-Louise", "George", "Omar", "Carol", "Deborah", "Joseph", "Ashleigh", "Emily", "Joyce", "Harry", "Marcus", "Bill", "Martin", "Luis", "Leo", "Byron", "Joseph", "John", "Julia", "Eric", "Thomas", "Pablo", "Lewis", "Willa", "Miguel", "Edith", "Tracy")
surname1 <- c("Chevalier", "Charles", "Chesterton", "Clay", "Cohen", "Collins", "Conway", "Cunningham", "Davis", "Daniels", "Douglas", "Evans", "Elliot", "Fields", "Ford", "Fox", "Gallagher", "Gibson", "Grant", "Harris", "Henry", "Hill", "Holmes", "Hunt", "James", "Jones", "Jensen", "Jennings", "Johnson", "Kay", "Kennedy", "King", "Lamb", "Lane", "Lee", "Lewis", "Locke", "Lynch", "MacArthur", "Mann", "Marin", "Martin", "Matthews", "May", "McCarthy", "McClary", "McGill", "McKay", "Mill", "Miller", "Mitchell", "Moore", "Morris", "Nelson", "Nicoll", "Ogilvy", "Ochs", "O'Brien", "Page", "Patterson", "Perry", "Phillips", "Ray", "Reed", "Rogers", "Russell", "Schiller", "Schultz", "Shelley", "Smith", "Snow", "Spencer", "Stein", "Star", "Stewart", "Stone", "Swift")
adj3 <- c("Disgraceful", "Terrible", "Horrible", "Devastating", "Sad", "Bloody")
emotion2 <- c("outraged", "upset", "extremely vexed", "so angry", "devastated")
sent7 <- c()
wish2 <- c("hope", "hope very much", "wish", "expect", "sincerely hope")
state2 <- c("dreadful state of affairs", "horrible pandemic", "all of the poor people dying", "tragedy")
time2 <- c("immediately", "very soon", "at once", "as soon as possible")
name2 <- c("Anna", "Luke", "Siobhan", "Su", "Ailidh", "Fiona", "Graham", "Madison", "Eleanor", "Rodrigo", "Kieran", "Wilson", "Anika", "Rosemary", "Alise", "Gordon", "Roman", "Karen")
verb2 <- c("devastate", "obliterate", "ruin", "destroy", "crush")
adj4 <- c("nearly", "almost", "virtually", "almost literally", "practically")


#set up person details for obits
x <- sample(1:2, 1)
if(x == 1){
pron1 <- "he"
posspron1 <- "his"
obit1name <- sample(c("Charles", "Robert", "Luke", "Phil", "George", "Elijah", "Noah", "William", "Ben", "James", "Henry", "Leo", "Luca", "Ray"), 1)
}
if(x == 2){
pron1 <- "she"
posspron1 <- "her"
obit1name <- sample(c("Dorothy", "Ellen", "Olivia", "Emma", "Charlotte", "Amelia", "Ava", "Sophia", "Millie", "Freya", "Poppy", "Sienna", "Florence"), 1)
}
obit1age <- sample(2:5, 1)
obit1like1 <- sample(c("jigsaw puzzles", "teddy bears", "dinosaurs", "airplanes", "books", "butterflies", "elephants", "hedgehogs", "horses", "fire engines", "penguins", "sail boats", "zebras"), 1)
obit1like2 <- sample(c("giraffes", "koala bears", "dragons", "cars", "movies", "goldfish", "trains", "unicorns", "winter", "trucks", "finger painting", "flowers", "sea turtles"), 1)
obit1siblings <- sample(c("Charlie, Alfie, and Jacob", "Tammy and Beth", "Theodore and Mason", "Rory and Susan", "William and Ethan", "Louise and Edward", "Caleb and Brody", "Carter, David, and Milo", "Billy and Parker", "Livvy and Jane"), 1)
obit1surname <- sample(c("Smith", "Jones", "Williams", "Taylor", "Davies", "Brown", "Wilson", "Evans", "Roberts", "Walker", "Wright", "Thompson", "Hughes", "Edwards", "Green", "Lewis", "Wood", "Martin", "Jackson", "Clark"), 1)


x <- sample(1:3, 1)
if(x == 1){
pron2 <- "he"
posspron2 <- "his"
obit2name <- sample(c("Edward", "Riley", "Hugo", "Ronnie", "Louis", "Grayson", "Caleb", "Benjamin", "Kai", "Jasper", "Albert", "Blake", "Dylan", "Liam"), 1)
}
if(x == 2){
pron2 <- "she"
posspron2 <- "her"
obit2name <- sample(c("Matilda", "Lucy", "Jessica", "Alice", "Maya", "Lottie", "Erin", "Maisie", "Bonnie", "Penelope", "Violet", "Esme", "Aurora"), 1)
}
if(x == 3){
pron2 <- "they"
posspron2 <- "their"
obit2name <- sample(c("Cypress", "Hollis", "Lex", "Landry", "Rory", "Salem", "Sol", "Kit", "Bellamy"), 1)
}

obit2age <- sample(50:90, 1)
obit2prof1 <- sample(c("musician", "author", "comedian", "artist"), 1)
obit2work1 <- sample(c("Green Grass", "A Whole Latte", "Golden Days", "One True Love", "Idle Thoughts", "Hopeless", "Purple Skies", "Framed", "Enemy of Fire", "Friends and Lovers", "My Best Friend", "A Fool's Errand", "Harmful", "Pigeons and Partridges"), 1)
obit2siblings <- sample(c("Luke and Chester", "Emily and Jonathan", "Gloria and Stephen", "Hester and Winifred", "Tammy, Theodore, and Thomas", "Frank and Thelma", "Eva and Elaine", "Charlotte and Harper", "Daisy and Phoebe", "Jim, Ella, and Evie"), 1)
obit2surname <- sample(c("Smith", "Jones", "Williams", "Taylor", "Davies", "Brown", "Wilson", "Evans", "Roberts", "Walker", "Wright", "Thompson", "Hughes", "Edwards", "Green", "Lewis", "Wood", "Martin", "Jackson", "Clark", "Campbell", "Burns", "Murphy", "Watt", "Marshall", "White", "Stevenson", "Young", "Watson", "Morrison", "King", "Bruce", "Hill", "Gibson", "Gordon"), 1)

```


<font size="+3"><b>`r city_name` `r sample(papername1, 1)`</b></font><br>
<font size="+2"><b>`r city_name` says farewell to pandemic's youngest victim</b></font><br>
by `r sample(authname1, 1)` `r sample(surname1, 1)`<br>
`r sample(pubdate, 1)`

The pandemic ravaging `r city_name` has claimed yet another victim. There have been `r outbreak_deaths4C` deaths in the pandemic so far, but perhaps the most tragic loss is `r obit1name` `r obit1surname` - at only `r obit1age`, the youngest victim that the pandemic has claimed.    

`r obit1name` `r obit1surname` liked `r obit1like1` and `r obit1like2`. Friends and family say that `r pron1` was always `r sample(c("a delight", "an absolute joy", "a treasure", "the most precious child"), 1)`. 

`r obit1name` is survived by `r posspron1` parents and grandparents, and by `r posspron1` siblings `r obit1siblings`. 

The funeral service will be held `r sample(c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday", "Saturday"), 1)` at `r sample(c("St. Ninian's", "Trinity Baptist Church", "Westlake Memorial", "St. Elfrida's Catholic Church", "St. Mary's", "Trinity Church", "St. Andrew's", "St. Judes"), 1)`.



:::

::: {.callout-caution collapse="true" icon=false}
## News/blog post #3 {.unnumbered}

<font size="+3"><b>`r city_name` `r sample(papername1, 1)`</b></font><br>
<font size="+2"><b>`r city_name` says farewell to local legend</b></font><br>
by `r sample(authname1, 1)` `r sample(surname1, 1)`<br>
`r sample(pubdate, 1)`

The `r dis_name` pandemic ravaging `r city_name` has claimed yet another victim. `r obit2name` `r obit2surname`, local `r obit2prof1` and star, sadly passed away on `r sample(c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday", "Saturday"), 1)`. 

`r obit2name` was perhaps best known for `r posspron2` `r sample(2000:2015, 1)` work `r obit2work1` , but fans say that the rest of `r posspron2` work was equally as `r sample(c("memorable", "genre-changing", "excellent", "influential"), 1)`. 

`r obit2name` is survived by `r posspron2` `r sample(c("partner", "husband", "wife"), 1)`, and by `r posspron2` siblings `r obit2siblings`. 

The funeral service will be held `r sample(c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday", "Saturday"), 1)` at `r sample(c("St. Ninian's", "Trinity Baptist Church", "Westlake Memorial", "St. Elfrida's Catholic Church", "St. Mary's", "Trinity Church", "St. Andrew's", "St. Judes"), 1)`.

:::

::: {.callout-caution collapse="true" icon=false}
## News/blog post #3 {.unnumbered}

<font size="+3"><b>`r city_name` `r sample(papername1, 1)`</b></font><br>
<font size="+2"><b>`r city_name` pandemic council making great strides</b></font><br>
by `r sample(authname1, 1)` `r sample(surname1, 1)`<br>
`r sample(pubdate, 1)`

Citizens of `r city_name` should be `r sample(c("grateful", "thankful", "glad"), 1)` that the city's Emergency Pandemic Response Committee, `r sample(c("swiftly", "quickly", "hurriedly"), 1)` convened when a new pandemic began to hit `r city_name`, has been so effective. While the initial death toll from the pandemic appeared to be quite `r sample(c("alarming", "devastating", "serious", "high", "heavy"), 1)`, the actions taken by the EPRC seem to have been sensible and will hopefully be effective. 

Officials from `r sample(c("the NHS", "Public Health Scotland", "the World Health Organisation", "the Center for Disease Control", "the Red Cross"), 1)` have publicly praised the `r city_name` EPRC, saying that `r sample(c("it is difficult to imagine a more effective public health response", "their actions have been extremely effective", "the EPRC has done all of the right things", "this is a triumph that shows how effective public health responses can be", "countless lives have been saved due to the actions of the EPRC"), 1)`

There do continue to be deaths occuring due to the pandemic, but hopefully `r city_name` will see the death toll begin to decrease in the coming weeks. 

:::



::: {.callout-caution collapse="true" icon=false}
## News/blog post #4 {.unnumbered}

<font size="+3"><b>`r city_name` `r sample(papername1, 1)`</b></font><br>
<font size="+2"><b>Yet more overreach in the name of "science"</b></font><br>
by `r sample(authname1, 1)` `r sample(surname1, 1)`<br>
`r sample(pubdate, 1)`

Governments across the globe have seen how successful power-grabs in the name of public health can be, following on the wave of restrictions imposed because of so-called viral diseases like COVID-19 and "mpox". So-called scientists are fearmongering - aerosols, monkeys, "bird" flu - now they think that they can fool us into thinking that the air and water are unsafe. Citizens of `r city_name` should stand strong against this terrible tyranny! No more mask mandates, no more senseless restrictions!

Our elders should not be left to die alone, left frightened and hopeless in a mandatory lockdown claimed to be "for their benefit." Vulnerable citizens should not be forced to cower in their homes, unable to engage in the most basic pleasures of daily life. 

Our children should not be left to struggle through "pandemic" after "pandemic" - their language and literacy skills have been left behind due to these lockdowns, and their mental health is suffering. 

Our businesses should not have to suffer because of this government overreach - already we have seen many close due to the COVID-19 "pandemic", it seems inevitable that this current "crisis" will cause many of our businesses to close as well. What happens to the economy of our fair city and the hard-working citizens who are unrightfully and unfairly losing their jobs due to this "Pandemic" committee's scaremongering?

It is time that we take back control of our lives and end this tyranny of fear-mongering and so-called science. Citizens of `r city_name`, stand with me and resist this most recent attack on your freedoms and your lives. Let's meet for a protest in front of City Hall this Saturday!

:::

::: {.callout-caution collapse="true" icon=false}
## News/blog post #5 {.unnumbered} 

<font size="+3"><b>`r sample(c("BBC Scotland", "The Guardian", "The Independent"), 1)` </b></font><br>
<font size="+2"><b>`r dis_name` pandemic in `r city_name`</b></font><br>
by `r sample(authname1, 1)` `r sample(surname1, 1)`<br>
`r sample(pubdate, 1)`

Hard on the heels of the COVID-19 pandemic and a number of other health scares (monkeypox, or "mpox", avian flu, and worries about other infectious disease outbreaks), another pandemic has hit the Scottish town of `r city_name`. This time, it's MRSA, a bacterium that can very sadly be fatal.

There have been `r outbreak_deaths4C` deaths in the pandemic so far, but perhaps the most frightening aspect to this new pandemic is rumours that these MRSA strains may have become resistant to even more antibiotics - a truly chilling possibility.

Scientists have been warning about the antibiotic resistance crisis for years, saying that careless use of antibiotics could mean that these precious medicines will no longer be available to us in the future. 

Some of the MRSA strains found in `r city_name` are reportedly resistant to all clinically available antibiotics, and scientists warn that these drug-resistant pathogens might be able to spread to new locations. Will nearby towns be next, or could these bacterial strains go as global as the SARS-COV2 virus did?

:::
